\LARGE \bf Mean Estimation from One-Bit Measurements

### 2020-12-01 adaptive-estimation.tex
missing \theta in proof of Thm. 5
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

\end{tikzpicture}
\end{center}
\caption{Distributed encoding with a single interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is to obtain another $n-n_1$ bits in a distributed manner. 
\label{fig:one_round}
}
\end{figure}

@@

  Now,
  Slutsky's lemmas imply
  \begin{equation}
    \sqrt{n}
    \cdot \frac{2}{n} \sum_{i = 1}^n (B_i - E_n)
    =
    (1 + o_P(1)) \frac{1}{\sqrt{n E_n(1 - E_n)}}
    \sum_{i = 1}^n \left(B_i - E_n\right)
    \cd \normal(0, 1).
    \label{eqn:apply-slutsky}
  \end{equation}
  For shorthand we write $P_n B = \frac{1}{n} \sum_{i = 1}^n B_i$,
  and using that $E_n = \E[B_i \mid T_n] = F(T_n - \theta)$, we may thus
  use the delta method to write
  \begin{align*}
    \sqrt{n}(\theta_n - \theta)
    & = \sqrt{n}\left(T_n - F^{-1}\left(P_n B\right)
    - \theta \right) \\
    & = \sqrt{n} \left(T_n - F^{-1}\left(F(T_n - \theta)
    + P_n B - F(T_n - \theta)\right) - \theta \right) \\
    & = \sqrt{n} \left(T_n - (T_n - \theta )
    + (F^{-1})'(T_n - \theta + o_P(1))\cdot \left(
    P_n B - E_n\right) \right) \\
    & = \sqrt{n} (F^{-1})'(0) (P_n B - E_n)
    + o_P(1)
    \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
  \end{align*}
  where we have used the limiting distribution~\eqref{eqn:apply-slutsky}.
\end{proof}
%

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
\begin{center}
\begin{tikzpicture}[scale = 0.6]
\begin{axis}[
width=10cm, height=6cm,
xmin = 0, xmax=800, 
restrict y to domain = 0:3,
ymin = 0,
ymax = 3.4,
samples=10, 
xlabel= $n$,
ylabel = {$n\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
%xtick={-3,-2,-1,0,1,2,3},
%xticklabels={-3,-2,-1,0,1,2,3},
ytick={0,1,1.57},
yticklabels={0,1,$\pi/2$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]

@@

\end{axis}
\end{tikzpicture}
\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density. In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$. The single interaction strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples for its first stage. 
\label{fig:adaptive_error}  }
\end{center}
\end{figure}

>>>>

\end{tikzpicture}
\end{center}
\caption{Distributed encoding with one round of interaction: The estimation obtained from the first $n_1$ bits in a distributed manner is utilized in obtaining another $n-n_1$ bits in a distributed manner. 
\label{fig:one_round}
}
\end{figure}

@@

  Now,
  Slutsky's lemmas imply
  \begin{equation}
    \sqrt{n}
    \cdot \frac{2}{n} \sum_{i = 1}^n (B_i - E_n)
    =
    (1 + o_P(1)) \frac{1}{\sqrt{n E_n(1 - E_n)}}
    \sum_{i = 1}^n \left(B_i - E_n\right)
    \cd \normal(0, 1).
    \label{eqn:apply-slutsky}
  \end{equation}
  For shorthand we write $P_n B = \frac{1}{n} \sum_{i = 1}^n B_i$,
  and using that $E_n = \E[B_i \mid T_n] = F(T_n - \theta)$, we may thus
  use the delta method to write
  \begin{align*}
    \sqrt{n}(\theta_n - \theta)
    & = \sqrt{n}\left(T_n - F^{-1}\left(P_n B\right)
    - \theta \right) \\
    & = \sqrt{n} \left(T_n - F^{-1}\left(F(T_n - \theta)
    + P_n B - F(T_n - \theta)\right) - \theta \right) \\
    & = \sqrt{n} \left(T_n - (T_n - \theta )
    + (F^{-1})'(T_n - \theta + o_P(1))\cdot \left(
    P_n B - E_n\right) - \theta \right) \\
    & = \sqrt{n} (F^{-1})'(0) (P_n B - E_n)
    + o_P(1)
    \cd \normal\left(0, \frac{1}{4 f(0)^2}\right),
  \end{align*}
  where we have used the limiting distribution~\eqref{eqn:apply-slutsky}.
\end{proof}
%

\begin{figure}
  %%%%% COMMENTED TIKZ PICTURE %%%%%
\begin{center}
\begin{tikzpicture}[scale = 0.6]
\begin{axis}[
width=10cm, height=6cm,
xmin = 200, xmax=800, 
restrict y to domain = 0:3,
ymin = 0,
ymax = 3.4,
samples=10, 
xlabel= $n$,
ylabel = {$n\cdot\mathbb E \left[\left(\theta - {\theta}_n \right)^2 \right]$},
%xtick={-3,-2,-1,0,1,2,3},
%xticklabels={-3,-2,-1,0,1,2,3},
ytick={0,1,1.57},
yticklabels={0,1,$\pi/2$},
line width=1.0pt,
mark size=1.5pt,
ymajorgrids,
xmajorgrids,
legend style= {at={(1,1)},anchor=north east,draw=black,fill=white,align=left}
]

@@

\end{axis}
\end{tikzpicture}
\caption{Normalized empirical risk versus number of samples $n$ for $10,000$ Monte Carlo trials with $f(x)$ the standard normal density. In each trial, $\theta$ is chosen uniformly over the interval $(-1.64,1.64)$. The one round threshold adaptation strategy uses $n_1 = \lfloor \sqrt{n} \rfloor$ samples before adapting the threshold.
\label{fig:adaptive_error}  }
\end{center}
\end{figure}

### 2020-12-01 conclusions.tex
Fixed typos. Updated Fig. "optimal density".  Rewrote Conclusions

\section{Conclusions \label{sec:conclusions}}
We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that no estimator can attain asymptotic relative efficiency larger than that of the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. 
%We also characterized the one-step optimal scheme in this adaptive setting, i.e., the scheme that minimizes the risk given any set of previously obtained bits.
\par
In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
%
These condition implies that, in the distributed, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting. 
%
We further considered the special case where the sequence of bits is obtained by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk.

>>>>

\section{Conclusions \label{sec:conclusions}}
We considered the risk and efficiency in estimating the mean of a symmetric and log-concave distribution from a sequence of bits, where each bit is obtained by encoding a single sample from this distribution. 
%
In an adaptive encoding setting, we showed that, asymptotically, no estimator can be more efficient than the median of the samples. We also showed that this bound is tight by presenting two adaptive encoding and estimation procedures that are as efficient as the median. Furtheremore, we showed that only one round of adapticity is required to attain the optimal efficiecny. In the distributed setting we provided conditions for local asymptotic normality of the encoded samples, which implies asymptotic minimax bound on both the risk and efficiency relative to the mean. 
%
Under local asymptotic normality, the optimal estimation performance derived for the adaptive case can only be attained over a finite number of points, i.e., no scheme is uniformly optimal in this setting. 
%
We further considered the special case where the sequence of bits is obtained in a distributed manner by comparing against a prescribed sequence of thresholds. We characterized the performance of the optimal estimator from such bit-sequence using the density of the thresholds and considered the density that minimizes the minimax risk. \par
Obvious extensions of our work include the derviation explicit bounds and optimal procedures when more than one-bit per sample is provided or when each sample is a vector. Another possible extension may consider estimation when single bits are sent between nodes of a directed graph.
